\section{Description}\label{description}

\paragraph{Arckane} uses powerfull computer science concepts to create an app where you can find teachers or offer teaching for every single skill in the world, Arckane proposes a distributed educational system where everyone can teach everyone, making it simple to charge for the tutoring services and to schedule teaching sessions. Teachers can also certify the specific skills they teach, with this Arckane can use the laws of offer and demand to create a fair global digital market of skills, users can charge for their skills securely and other people or organizations can find profiles with specific skill sets automatically. Think about it as the Uber or Airbnb of education and work.

\paragraph{} Arckane is a technology corporation dedicated to enhance how education is achieved (distribution of knowledge and skills), make that adquired knowledge extremely useful and convert the whole process into something fun. Arckane is actually attacking two industries, the education industry and the recruiting industry.

\paragraph{} The education industry has been widely satisfied in two main forms, the creation of educational systems and the creation of tools to enhance these systems. We can enlist 3 main educational systems, the traditional system where students assist to institutions and listen to teachers in a hierarchical social structure, autodidactism where the students use media like books or web resources to teach themselves, and online courses which is a hybrid between the first two and uses the power of the internet to provide massive reach, these three systems provide a structure on which a person can acquire knowledge and skills and also some degree of certification, which functions as a system to communicate the skills of the student to other persons or organizations. The second widely form in which the education industry has been satisfied is the creation of educational tools, specially software tools like Wikipedia, online course platforms or domain specific apps. The way Arckane seeks to enhance world wide education is by proposing a fourth educational system, one that is orders of magnitudes better because: 1) it creates a digital platform which uses powerful computer science concepts to automate education, certification and the offering of those skills to the world after education is achieved, 2) it proposes a much better social structure for the flow of knowledge, making knowledge viral between society, 3) enables a much better economic system, making education much more economically feasible for everyone, creating economic opportunities for users and giving an extraordinary business model to Arckane. 

\paragraph{} The recruiting industry has recently been digitalized to a certain extent by social networks like Facebook or LinkedIn, but still all sizes of companies have to spend too much money, time and resources into finding the right talent. The problem is that to truly automate recruiting the system must know in detail the skill profile of each person and the specific requirements of skills of the organizations and projects, in a way in which the recruiter can be sure that the recruitee actually has the right level of proficiency in such skills, that is why even though social networks are great tools for finding people it is still a manual picking process and not an automated reliable one. Arckane uses the power behind the digitalized distributed education system to create a digital market of skills, one in which the system granularly knows what everyone knows, and by using the laws of offer and demand it can give accurate information of the value of specific skill sets, also this allows for automatic matchmaking, organizations and projects can query the system for persons with specific skill sets who are looking to do something with them, and the persons with skills can automatically find interesting jobs and projects. The distributed education system also is complemented because organizations can certify the skills their employees are obtaining and gain reputation for it, making it more attractive for new employees. All of this made reliable and objective by powerful computer science concepts.     

\paragraph{Mission:} Make knowledge universally accessible, useful and fun.

\paragraph{Vision:} A world where acquiring, sharing and using knowledge is simple, automatic and fun for every single person thanks to the technology and institutes created by Arckane, a world where every skill is developed on demand.


