% Justification

\section{Justification}\label{justification}

\paragraph{} As mentioned in the description there exist 3 main educational systems nowadays, in this section we will enlist the pros and cons of each system and how Arckane solves these issues and retains the desired properties at the same time.

\subsection{Traditional System Pros}
\begin{enumerate}
\item Teachers and students have direct social interaction with each other.
\item Best certification system in comparison with the other two systems.
\item Widely researched by education sciences.
\end{enumerate} 

\subsection{Traditional System Cons}
\begin{enumerate}
\item Extremely bad economical system, students, families and the government have to invest from 20-25 years and millions of dollars in giving a generic amount of skills to a person, skills that when entering the market may lack or never be used. 
\item Bad social structure, by creating a hierarchical structure education flow is damped. (see appendix A: graphs and education)
\item Even though it has the best certification system, the system is not digital, global, automated or even sometimes objective.
\item Lack of customizability, students have to learn what told and for professional education they have to wait for a university to offer the right program.
\end{enumerate} 

 \subsection{Autodidactism Pros}
\begin{enumerate}
\item Most customizable education system, the students adapts to whatever fits him the best.
\item Education becomes “on demand” which means that the student learns what he wants or thinks he needs in the moment.
\item Is extremely cheap.
\end{enumerate} 

\subsection{Autodidactism Cons}
\begin{enumerate}
\item Hard to find a social environment, which is crucial for education.
\item Inexistent certification system.
\item Hard to approach because the lack of guidance.
\end{enumerate} 

\subsection{Online Courses Hybrid Pros and Cons}
\begin{enumerate}
\item Has massive reach thanks to the online platforms.
\item Education is more customizable than traditional but less than autodidactism.
\item Social interaction is more than autodidactism but less than traditional.
\item Certification system is better than autodidactism but worst than traditional.
\item Has better guidance than autodidactism but worst than traditional. 
\end{enumerate} 

% Arckane Holistic Solution

\subsection{Arckane Holistic Solution}

(A complete description of the distributed system is given at section) Arckane addresses the issues enlisted in the last subsections by giving a holistic solution, which means that its technologies does not just focus on education, but also in making knowledge useful after education is achieved by creating a healthy world wide digital market for the usage of skills and knowledge. Lets see first how Arckane solves each enlisted issue:

\paragraph{Traditional system issue:} Extremely bad economical system.
\paragraph{Arckane solution:} The distributed education system and the online platform allows to offer education on demand, students develop granular skills as needed or as desired, so for example if a student wants to learn to manage Oracle databases instead of having to go through a Computer Science bachelors he can find the best rated tutors nearby and develop those exact skills, the student will only pay for objective tutoring hours and can immediately use the skills after the education is accomplished. Also organizations can publish the skill profiles they are looking for so that students develop the exact set of skills needed, against developing skills that they may not use and therefore waste their money developing them. As the distributed tutor does not need to be part of a huge bureaucratic institution his hourly rate can be much lower, offering quality education at lower cost.

\paragraph{Traditional system issue:} Bad social structure.
\paragraph{Arckane solution:} (See appendix: graphs and education for more detailed information) The distributed education system maintains the scale free properties of the social graph keeping the viral capacity of the former, plus it does not limit someone to teach another and brings economical opportunity to whoever wants to give quality education under a reputation and rating system, incentivising the tutors to always try to be better tutors. Anyone can teach and be teached in the same day multiple times.

\paragraph{Traditional system issue:} Lack of customizability.
\paragraph{Arckane solution:} Since the tutors in the distributed education system are personal and get a detailed profile of each student the education can be highly customizable, using machine learning techniques the system can learn how a student learns, with this Arckane can recommend the best resources for the student and make a perfect matchmaking between tutors and apprentices.

\paragraph{Autodidactism issue:} Lack of social interaction.
\paragraph{Arckane solution:} The distributed education system is even more social than the traditional system, in the traditional system students go to institutions where most of the time they are prohibited to interact (when in lectures), in the distributed system there is constant interaction between the tutor and the apprentice and the other apprentices the tutor may have. Also since Arckane “knows what everyone knows” (given by the ratings of the skills of the apprentice or the skills a tutor teaches) we can create features which promote social interaction like events over things that matter, like sports, sciences or arts. 

\paragraph{Autodidactism issue:} Lack of guidance.
\paragraph{Arckane solution:} The bedrock of the distributed education system is to exploit the power of social interaction, of finding the best tutors or guiders, its highly customizability, social interaction and digital automation allows to find great people who can guide the apprentice through whatever path he is choosing to take.

\paragraph{General issue:} Lack of a digital, automated, global and objective certification system.
\paragraph{Arckane solution:} Arckane uses the power of technology to bring not just the automated matchmaking of tutors and apprentices, but also an objective reputation-based certification system where an apprentice gets certificated not by one organization, but by the set of all tutors he have been using, and the certifications tutors give are more powerful thanks to 3 main features: 1) it is reputation based, which means that the certification of skill that gives a badly rated tutor has almost no value against the best rated tutors. 2) it is based on 5 ratings: introductory, basic, medium, advanced and expert, giving not a “bad” vs “good” label, but communicating the exact level of proficiency of the apprentice. And 3) it is digital, which means that Arckane can go beyond certificating and create a system where apprentices can exploit everything they have learned, it creates a digital market of skills, where apprentices can easily, fairly and automatically offer and charge for their skills, and people or organizations that are looking for an exact set of skills can automatically find people with the desired rating. Then apprentices can go beyond and get rating for their skills from the projects and organizations they have been working on, reflecting their new proficiency levels and the new skills obtained while working.

